\papertitle

### 2012-10-12 manuscript.tex
Start on Pose Estimation

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
%TODO ryan

%TODO trim PDF
\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{CAPTION.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}

>>>>

%----------------------------------------------------------------------------%
\subsection{Pose Estimation}
%TODO ryan
The ground station performs simple two-dimensional pose estimation on the H$^2$Bird using 
a particle filter-based motion tracking algorithm. This pose estimate is 
the feedback input to the cooperative visual servoing feedback loop (Sec. \ref{sec:visual_servoing_concept}).

We limit our pose estimation approach to monocular two-dimensional object 
tracking in pixel-space. This allows us to perform high-rate video tracking 
using the modest computational resources available on the ground station, 
and similarly millirobotic ground vehicles.

~\cite{thrun2005probabilistic}

%----------------------------------------------------------------------------%
\subsection{Visual Servoing}
\label{sec:visual_servoing_concept}
%TODO ryan

\begin{figure}[tb]
\centering
\includegraphics[width=\linewidth]{figures/block_diagrams.pdf}
\caption{Overall block diagram of the cooperative control system.}
\label{fig:block_diagram}
\end{figure}

@@

\begin{figure*}[tb]
\begin{minipage}[b]{0.45\linewidth}
\includegraphics[width=\textwidth]{figures/feasible_set.pdf}
\caption{Plot of backwards reachable set for successful window traversal.}
\label{fig:feasible_set}
\end{minipage}
\hfill
\begin{minipage}[b]{0.45\linewidth}
\centering
\centering
\includegraphics[width=\textwidth]{figures/heat_map.pdf}
\caption{Probability of success for all starting locations. This graphic is 
a result of a Monte Carlo simulation of the reachable set model, in which the 
initial heading of the H$^2$Bird is chosen uniformly at random from $(-90,90)$.}
\label{fig:heat_map}
\end{minipage}
\end{figure*}
